%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

% Instructions:
% Demonstrate rather than describe. Highlight impact and decision making.

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Cofounder \& Chief Data Scientist} % Job title
    {Ansaro} % Organization
    {San Francisco, CA} % Location
    {Jun. 2017 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped define Ansaro's cultural foundation by establishing mission, values, and feedback/reflection sessions from the beginning.}
        \item {Led all aspects of data science-related efforts including scoping projects, dev environment automation, analysis, model training/versioning, and communicating results.}
        \item {Developed the content for Ansaro's structured interview platform, nearly 200 interview questions across 16 topic areas, based on academic research related to job performance predictive validity.}
        \item {Created the web app POC of Ansaro's \textit{AI Notetaker} (interview audio recording and transcription). Conducted user research to design this feature. Our team then developed this in the Ansaro platform, enabling collection of valuable interview content.}
        \item {Developed and delivered interpretable machine learning models for Teach For America (an Ansaro customer) to predict application withdrawal risk based on applicant information and written essays.}
        \item {Built and ran the pipeline to parse information from 800,000+ resumes into structured data for Dropbox (an Ansaro customer), standardize the parsed data, and upload to Greenhouse, to understand hiring patterns and drivers of quality of hire.}
        \item {Planned and executed a project for a Harvard Business School professor that explored and analyzed a large text corpus using topic modeling and classifiers to surface temporal trends of how women are treated in the workplace (research ongoing).}
        \item {Contributed to the {\href{https://medium.com/ansaro-blog}{company blog}}, communicating ideas that are important to our company, particularly related to people analytics and data science.}
        % \item {Developed a quality-of-hire metric for Andeavor (an Ansaro customer) to track company and department performance before and after using the Ansaro platform for hiring.}
        % Cares deeply about being an effective and respectful cofounder and teammate.
        % % reevaluating as necessary
        % , and embedding this in our company culture, making Ansaro a place people want to work.
        % \item { including scoping nebulous project into concrete goals, dev environment automation, data analysis, training and interpreting machine learning models (supervised \& unsupervised, classification \& regression, NLP), model versioning/serialization, and communicating results.}
        % \item {Turns nebulous customer problems into concrete projects with clear goals and timelines.}
        % \item {Conducts academic literature searches to develop product content, and performs user research to guide UX decisions.}
        % \item {Builds tools and pipelines across the product lifecycle, from product and feature POCs to production-level processes.}
        % \item {Interprets and communicates the business trade-offs of ML model choices.}
     \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Freelance Consultant} % Organization
    {San Francisco, CA} % Location
    {Apr. 2017 -- May 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Strategic planning for the analysis and processing/machine learning pipeline for a new sports-related mobile application.} % Ped Motion
        \item {Analyzed time series motion sensor data collected with the mobile phone app.}
        \item {Trained and assessed machine learning models to predict current user behavior based on motion data.}
        \item {Supervised an Insight Data Science fellow in using the pipeline and models that I developed, in their project.} % Phil Gaudreau
     \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Lead Scientist} % Job title
%     {\href{https://github.com/sfbrigade/data-science-wg}{Code for San Francisco, Data Science Working Group}} % Organization
%     {San Francisco, CA} % Location
%     {Feb. 2016 -- Jun. 2017} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Volunteered at a weekly meetup to work on and oversee projects that solve problems involving civic issues and open data.}
%         \item {Helped assure statistical and technical quality and helped educate volunteers who are new to the group.}
%       \end{cvitems}
%     }

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Silicon Valley Data Science} % Organization
    {Mountain View, CA} % Location
    {Jan. 2015 -- Mar. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Trained deep neural networks (RNN/LSTM) to create a speech recognition system, which was the seed R\&D for a {\href{https://www.lexicon.ai}{spinout company}}.} % LexiconAI / LexiconRN
        \item {Developed and deployed predictive models to production at a major global company, the results of which surfaced insights about customer behavior related to churn, purchasing patterns, fraud, and more.} % Nike
        \item {Created a process to train time series models (ARIMA) to forecast sales figures at a large energy company. The models reduced sales forecast error for the most recent quarter by 19.5\% (roughly \$30MM).} % Schneider Electric
        \item {Helped develop a data strategy report at a large technology hardware manufacturing and supply chain management company. Through onsite research and interviews, the report detailed how to adapt and expand current data collection practices to provide analytics and data services across their verticals (retail, manufacturing, healthcare, transportation \& logistics).} % Zebra Technologies
        \item {Detected anomalous behavior in multi-terabyte system logs at a provider for the global travel and tourism industry.} % Amadeus IT Group
        \item {Co-developed an ARIMA time series modeling tutorial, presented at {\href{https://pydata.org/sfo2016/schedule/presentation/38/}{PyData SF 2016}}.}
        % {\href{https://www.youtube.com/watch?v=tJ-O3hk1vRw}{(video recording})}
        % {\href{https://github.com/silicon-valley-data-science/pydata-sf-2016-arima-tutorial}{(GitHub repo no longer available})}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fellow} % Job title
    {Insight Data Science} % Organization
    {Palo Alto, CA} % Location
    {Sep. 2014 -- Nov. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created \textit{This Is Happening}, a website for finding social events happening now.}
        \item {Detected events in real-time by streaming social media activity into a database and comparing current activity to baseline levels.  Pockets of activity were used as seed locations for a clustering algorithm to label events.}
        \item {Summarized event topics using NLP, and made API calls to retrieve nearby social media (Twitter, Instagram).}
        \item {Deployed the front-end using Flask, Bootstrap, jQuery, JavaScript, HTML, CSS, and AWS.}
      \end{cvitems}
    }

% %---------------------------------------------------------
%   \cventry
%     {Graduate Researcher} % Job title
%     {University of Colorado Boulder} % Organization
%     {Boulder, CO} % Location
%     {2008 -- 2015} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Employed statistical and machine learning techniques on neural and behavioral data to assess hypotheses about memory formation, with implications for improving studying strategies in the real world.}
%         \item {Communicated findings via publications and conference talks to greater psychological community.}
%         \item {Developed a MATLAB software package for organizing and analyzing neural data.}
%         \item {Developed a MATLAB software framework for running psychology experiments.}
%         \item {Programmed experiments in MATLAB and Python for studying human memory.}
%         \item {Course instructor for \textit{Introduction to Cognitive Psychology}.}
%         \item {Teaching assistant for \textit{Statistics}.}
%       \end{cvitems}
%     }

% %---------------------------------------------------------
%   \cventry
%     {Lab manager and researcher} % Job title
%     {University of Pennsylvania} % Organization
%     {Philadelphia, PA} % Location
%     {2005 -- 2008} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Programmed experiments in Python for studying memory and spatial navigation in humans.}
%         \item {Analyzed behavioral and neural data recorded during memory tasks.}
%         \item {Coordinated research and lab business with collaborators (principal investigators, graduate students, and undergrads) at institutions around the US.}
%         \item {Presented research both at international conferences and in peer-reviewed publications.}
%       \end{cvitems}
%     }

% %---------------------------------------------------------
%   \cventry
%     {Undergraduate research assistant} % Job title
%     {Brandeis University} % Organization
%     {Waltham, MA} % Location
%     {2002 -- 2005} % Date(s)
%     {
%       \begin{cvitems} % Description(s) of tasks/responsibilities
%         \item {Conducted an experiment investigating neural correlates of high-level perception in a spatial navigation task.}
%         \item {Analyzed data from the spatial navigation experiment, culminating in an honors thesis and subsequent publication.}
%       \end{cvitems}
%     }

%---------------------------------------------------------
\end{cventries}
